---
title: "Basic Diagnostics"
author: Ann Wells
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    keep_md: TRUE
    code_folding: hide
    collapsed: no
    toc: yes
    toc_float: yes
    self_contained: no
   
---

# Introduction and Data files
```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
options(stringsAsFactors = F)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(progress=FALSE)
```

## Data and analysis description

This dataset contains nine tissues (heart, hippocampus, hypothalamus, kidney, liver, prefrontal cortex, skeletal muscle, small intestine, and spleen) from C57BL/6J mice that were fed 2-deoxyglucose (6g/L) through their drinking water for 96hrs or 4wks. The organs from the mice were harvested and processed for metabolomics and transcriptomics. The data in this document pertains to the transcriptomics data only. This document specifically only calculates and plots principal component analysis for log transformed data. 

```{r load packages}
needed.packages <- c("tidyverse", "here", "functional", "gplots", "dplyr", "GeneOverlap", "R.utils", "reshape2","magrittr","data.table", "RColorBrewer","preprocessCore","plotly")
for(i in 1:length(needed.packages)){library(needed.packages[i], character.only = TRUE)}
```

```{r read in data, eval=FALSE}
setwd(here("Data","counts"))

files <- dir(pattern = "*.txt")

data <- files %>% map(read_table2) %>% reduce(full_join, by="gene_id")

tdata <- t(sapply(data, as.numeric))

tdata.FPKM <- grep("FPKM", rownames(tdata)) 

tdata.FPKM <- tdata[tdata.FPKM,]

colnames(tdata.FPKM) <- data$gene_id

tdata.FPKM <-tdata.FPKM[,colSums(tdata.FPKM) > 0]

# Read all the files and create a FileName column to store filenames
DT <- rbindlist(sapply(files, fread, simplify = FALSE),
                use.names = TRUE, idcol = "FileName")

name <- strsplit(DT$FileName,"_")

samples <-c()
for(i in 1:length(name)){
samples[[i]] <- as.list(paste(name[[i]][1],name[[i]][2], sep="_"))
}

sampleID <- unique(rapply(samples, function(x) head(x,c(1))))

names <- unique(rapply(name, function(x) head(x,c(1))))
#names.samples <- c(names, names[12], names[14], names[17], names[37], names[41], names[11], names[49])
names.samples <- sort(names)
tdata.FPKM.names.samples <- cbind(names.samples, tdata.FPKM)
rownames(tdata.FPKM.names.samples) <- names
rownames(tdata.FPKM) <- names
#lengthID <- table(sampleID)

sample.info <- read_csv(here("Data","Sample_layout_RNAseq_mouse_ID_B6_96hr_4wk.csv"))
#sample.info.duplicated <- rbind(sample.info[16,], sample.info[17,], sample.info[21,], sample.info[27,], sample.info[54,],
#                                sample.info[60,], sample.info[70,], sample.info)
#sample.info.duplicated <- sample.info.duplicated %>% arrange(`Sample ID`)

tdata.FPKM.names.samples <- rownames_to_column(as.data.frame(tdata.FPKM.names.samples)) # %>% mutate("Sample ID" = rownames(tdata.FPKM))

tdata.FPKM.sample.info <- left_join(tdata.FPKM.names.samples, sample.info, by = c("names.samples" = "Sample ID"))

rownames(tdata.FPKM.sample.info) <- names

saveRDS(tdata.FPKM.sample.info[,-c(1:2)], here("Data", "20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

saveRDS(tdata.FPKM, here("Data", "20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

```

***

# PCA (logged all data) {.tabset .tabset-fade .tabset-pills}
These plots contain all tissues, treatments, and times.

```{r PCA logged all data, cache=TRUE,child='knitr-pca-logged-all-data.Rmd'}
```

***

# PCA (log Time) {.tabset .tabset-fade .tabset-pills}
These plots subset the data so all tissues and treatments are plotted for a single time point.

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-single-timepoint.Rmd'}
```

***

# PCA (log Treatment) {.tabset .tabset-fade .tabset-pills}
These plots use subsetted data so the dataset plotted contains all tissues and time points per treatment type (2DG or control).

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-single-treatment.Rmd'}
```

***

# PCA (log Tissue) {.tabset .tabset-fade .tabset-pills}
These plots subset the data so each plot contains treatment and time for each tissue.

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-single-tissue.Rmd'}
```

***

# PCA (log Tissue 96hr 2DG) {.tabset .tabset-fade .tabset-pills}
These plots subset the data so each plot contains mice treated with 2DG for 96hrs for each tissue.

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-96hr-2DG-tissue.Rmd'}
```

***

# PCA (log Tissue 96hr control) {.tabset .tabset-fade .tabset-pills}
These plots subset the data so each plot contains mice treated with nothing for 96hrs for each tissue.

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-96hr-control-tissue.Rmd'}
```

***

# PCA (log Tissue 4wk 2DG) {.tabset .tabset-fade .tabset-pills}
These plots subset the data so each plot contains mice treated with 2DG for 4wks for each tissue.

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-4wk-2DG-tissue.Rmd'}
```

***

# PCA (log Tissue 4wk control) {.tabset .tabset-fade .tabset-pills}
These plots subset the data so each plot contains mice treated with nothing for 4wks for each tissue.

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-4wk-control-tissue.Rmd'}
```

***

# PCA (log Treatment by tissue 96hr) {.tabset .tabset-fade .tabset-pills}
These plots subset the data so each plot contains mice that were treated or untreated for 96hrs for each tissue.

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-treatment-tissue-96hr.Rmd'}
```

***

# PCA (log Treatment by tissue 4wk) {.tabset .tabset-fade .tabset-pills}
These plots subset the data so each plot contains mice that were treated or untreated for 4wks for each tissue.

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-treatment-tissue-4wk.Rmd'}
```

***

# PCA (log Time by tissue 2DG) {.tabset .tabset-fade .tabset-pills}
These plots subset the data so each plot contains mice that were treated with 2DG for 96hrs or 4wks for each tissue.

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-time-tissue-2DG.Rmd'}
```

***

# PCA (log Time by tissue control) {.tabset .tabset-fade .tabset-pills}
These plots subset the data so each plot contains mice that were treated with nothing for 96hrs or 4wks for each tissue.

```{r PCA logged time, cache=TRUE, child='knitr-pca-logged-time-tissue-control.Rmd'}
```

***
