---
title: "Module Generation SM.SI.spleen"
author: Ann Wells
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
   keep_md: TRUE
   code_folding: hide
   collapsed: no
   toc: yes
   toc_float: yes
   self_contained: no
---

<link rel="stylesheet" type="text/css" href="https://cdn.datatables.net/1.10.5/css/jquery.dataTables.min.css">
<script src="https://code.jquery.com/jquery-2.1.2.min.js"></script>
<script src="https://cdn.datatables.net/1.10.5/js/jquery.dataTables.min.js"></script>

<script type="text/javascript">
         $(document).ready(function() {
             $("table").DataTable();
         } );
</script>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
options(stringsAsFactors = F)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(progress=FALSE)

needed.packages <- c("tidyverse", "here", "functional", "gplots", "dplyr", "GeneOverlap", "R.utils", "reshape2","magrittr","data.table", "RColorBrewer","preprocessCore", "ARTool","emmeans", "phia", "gProfileR", "WGCNA", "xtable","downloadthis")
for(i in 1:length(needed.packages)){library(needed.packages[i], character.only = TRUE)}

source(here("source_files","plot_theme.R"))
source(here("source_files","WGCNA_source.R"))
```

```{r load_data}
log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA <- readRDS(here("Data","SM.SI.spleen","log.tdata.FPKM.sample.info.subset.SM.SI.spleen.missing.WGCNA.RData"))
```

## Set Up Environment

The WGCNA package requires some strict R session environment set up.

```{r}
options(stringsAsFactors=FALSE)

# Run the following only if running from terminal
# Does NOT work in RStudio
#enableWGCNAThreads()
```

## Choosing Soft-Thresholding Power {.tabset .tabset-fade .tabset-pills}

WGCNA uses a smooth softmax function to force a scale-free topology on the gene expression network. I cycled through a set of threshold power values to see which one is the best for the specific topology. As recommended by the authors, I choose the smallest power such that the scale-free topology correlation attempts to hit 0.9.

```{r, include=FALSE}
powers <- 1:20
  
soft <- pickSoftThreshold(log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA, powerVector=powers, verbose=0)
```

```{r, cache=TRUE, results='asis'}
threshold <- softthreshold(soft)

```

### Pick Soft Threshold

```{r}
knitr::kable(soft$fitIndices)

soft$fitIndices %>%
  download_this(
    output_name = "Soft Threshold SM SI spleen",
    output_extension = ".csv",
    button_label = "Download data as csv",
    button_type = "info",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
```

## Calculate Adjacency Matrix and Topological Overlap Matrix

I generated a weighted adjacency matrix for the gene expression profile network using the softmax threshold I determined in the previous step. Then I generate the Topological Overlap Matrix (TOM) for the adjacency matrix. This reduces noise and spurious associations according to the authors.I use the TOM matrix to cluster the profiles of each metabolite based on their similarity. I use dynamic tree cutting to generate modules. 

```{r adjacency matrix, cache=TRUE, cache.lazy=FALSE}
soft.power <- which(soft$fitIndices$SFT.R.sq >= 0.88)[1]
cat("\n", "Power chosen") 
soft.power
cat("\n \n")

adj.mtx <- adjacency(log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA, power=soft.power)

TOM = TOMsimilarity(adj.mtx)
diss.TOM = 1 - TOM

metabolite.clust <- hclust(as.dist(diss.TOM), method="average")

min.module.size <- 15

modules <- cutreeDynamic(dendro=metabolite.clust, distM=diss.TOM, deepSplit=2, pamRespectsDendro=FALSE, minClusterSize=min.module.size)

# Plot modules
cols <- labels2colors(modules)
table(cols)

plotDendroAndColors(
  metabolite.clust, cols, xlab="", sub="", main="Gene Clustering on TOM-based Similarity", 
  dendroLabels=FALSE, hang=0.03, addGuide=TRUE, guideHang=0.05
)
```

## Merging Related Modules

Some modules might be highly correlated. The authors recommend merging modules with a correlation greater than 0.75.

```{r}
me.list <- moduleEigengenes(log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA, colors=cols) 
me <- me.list$eigengenes

# Eigenmetabolite dissimilarity
me.diss <- 1 - cor(me)

h <- hclust(as.dist(me.diss), method="average")

# Merge threshold = 1 - correlation threshold
merge.thresh <- 0.25

plot(h, main="Clustering of Module Eigengene", xlab="", sub="")
abline(h=merge.thresh, col="red")

merge <- mergeCloseModules(log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA, cols, cutHeight=merge.thresh, verbose=0)
merged.cols <- merge$colors
merged.mes <- merge$newMEs

  # Check how the merging changed the clustering of the metabolites
plotDendroAndColors(
  metabolite.clust, cbind(cols, merged.cols), c("Dynamic Tree Cut", "Merged Dynamic"), xlab="", sub="", 
  main="Gene Clustering on TOM-based Similarity", 
  dendroLabels=FALSE, hang=0.03, addGuide=TRUE, guideHang=0.05
  )
```

## Calculating Intramodular Connectivity

This function in WGCNA calculates the total connectivity of a node (metabolite) in the network. The kTotal column specifies this connectivity. The kWithin column specifies the node connectivity within its module. The kOut column specifies the difference between kTotal and kWithin. Generally, the out degree should be lower than the within degree, since the WGCNA procedure groups similar metabolite profiles together.

```{r}
net.deg <- intramodularConnectivity(adj.mtx, merged.cols)
saveRDS(net.deg,here("Data","SM.SI.spleen","Chang_2DG_BL6_connectivity_SM_SI_spleen.RData"))
head(net.deg)
```

## Summary


The dataset generated coexpression modules of the following sizes. The grey submodule represents metabolites that did not fit well into any of the modules. 

```{r}
table(merged.cols)
```

```{r}
# Module names in descending order of size
module.labels <- names(table(merged.cols))[order(table(merged.cols), decreasing=T)]
# Order eigenmetabolites by module labels
merged.mes <- merged.mes[,paste0("ME", module.labels)]
colnames(merged.mes) <- paste0("log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA_", module.labels)
module.eigens <- merged.mes
# Add log.tdata.FPKM.sample.info.subset.WGCNA tag to labels
module.labels <- paste0("log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA_", module.labels)

# Generate and store metabolite membership
module.membership <- data.frame(
  Gene=colnames(log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA),
  Module=paste0("log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA_", merged.cols)
)

saveRDS(module.labels, here("Data","SM.SI.spleen","log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA.module.labels.RData"))
saveRDS(module.eigens, here("Data","SM.SI.spleen","log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA.module.eigens.RData"))
saveRDS(module.membership, here("Data","SM.SI.spleen", "log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA.module.membership.RData"))

write.table(module.labels, here("Data","SM.SI.spleen","log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA.module.labels.csv"), row.names=F, col.names=F, sep=",")
write.csv(module.eigens, here("Data","SM.SI.spleen","log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA.module.eigens.csv"))
write.csv(module.membership, here("Data","SM.SI.spleen","log.tdata.FPKM.sample.info.subset.SM.SI.spleen.WGCNA.module.membership.csv"), row.names=F)
```

