---
title: "Summary Kidney"
author: Ann Wells
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
   keep_md: TRUE
   code_folding: hide
   collapsed: no
   toc: yes
   toc_float: yes
   self_contained: no
   
---


# Summary

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
options(stringsAsFactors = F)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(progress=FALSE)

```

```{r load packages}
needed.packages <- c("tidyverse", "here", "functional", "gplots", "dplyr", "GeneOverlap", "R.utils", "reshape2","magrittr","data.table", "RColorBrewer","preprocessCore", "ARTool","emmeans", "phia", "gProfileR","rlist", "pheatmap", "WGCNA")
for(i in 1:length(needed.packages)){library(needed.packages[i], character.only = TRUE)}

source(here("source_files","WGCNA_source.R"))
```

There were 16 samples (4 per time and treatment). Mice were fed 2DG (6g/L) or nothing in their water for 96hrs or 2 weeks. WGCNA analysis was performed to determine gene clustering. A soft-thresholding power was chosen so that the scale-free topology correlation attempts to hit 0.9. The power chosen for kidney was 3, which allowed the correlations to hover around 0.90. This power clustered the genes into 24 modules originally, however, modules that were highly correlated (0.75 or higher) were further merged together to create 17 modules.

```{r, cache=TRUE}
modules<-read.csv(here("Data","Kidney","log.tdata.FPKM.sample.info.subset.kidney.WGCNA.module.membership.csv"), header=T)

module_barplot(modules)
```

## Pathways {.tabset .tabset-fade .tabset-pills}
Pathways were assessed for each module. Out of 17 modules, only 12 modules had pathway hits of any kind. The pathways that had the highest frequency across modules were metabolic pathways and collagen. The blue, cyan, pink, and red modules all contained these pathways.

### Blue

47 pathways were identified for the **blue** module. The pathways identified were involved in cell cycle, BCAA metabolism, DNA pathways, general metabolism, post-translational modification, and Class 1 MHC processing and presentation.

### Cyan
107 pathways identified for the **cyan** module. The pathways identified were involved in several cancers, insulin signaling, toll like receptors, and cancer pathways.

### Darkgreen module

12 pathways were identified for the **darkgreen** module. The pathways identified were involved in DNA repair, PPAR signaling, and protein digestion and absorption.

### Darkgrey

2 pathways were identified for the **darkgrey** module, ABC transporters and neurotrophin signaling pathway.

### Darkred

2 pathways were identified for the **darkred** module, SLC-mediated transmembrane transport and transport of small molecules.

### Darkturquoise

11 pathways were identified for the **darkturquoise** module. The pathways identified were involved in collagen, extracellular matrix, calcium and potassium channels, and protein digestion and absorption.

### Grey60

4 pathways were identified for the **grey60** module. The pathways involved were glutamatergic synapse, neurexins and neuroligins, neuronal system, and protein-protein interactions at synapses.

### Lightgreen

2 pathways were identified for the **lightgreen** module, potassium channels and voltage gated potassium channels.


### Lightyellow

3 pathways were identified for the **lightyellow** module, mitotic spindle checkpoint, phosphorylation of the APC/C, regulation fo APC/C activators between G1/S and early anaphase.

### Magenta

3 pathways were identified for the **magenta** module, arrhythmogenic right ventricular cardiomyopathy, muscle contraction, and striated muscle contraction.

### Pink

73 pathways were identified for the **pink** module.  The pathways identified were involved in bile acid metabolism, chylomicron pathways, complement pathways, HDL pathways, innate immunity, general metabolism, plasma pathways, and VLDL pathways.

### Red

101 pathways were identified for the **red** module. The pathways identified were involved in Alzheimer's disease, external cellular response (hypoxia, stress), general metabolism, mRNA and RNA pathways, NAFLD, and triglyceride biosynthesis.

```{r}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

log.tdata.FPKM.sample.info <- cbind(log.tdata.FPKM, tdata.FPKM.sample.info[,27238:27240])

log.tdata.FPKM.sample.info <- log.tdata.FPKM.sample.info %>% rownames_to_column() %>% filter(rowname != "A113") %>% column_to_rownames()

log.tdata.FPKM.subset <- log.tdata.FPKM[,colMeans(log.tdata.FPKM != 0) > 0.5] 

log.tdata.FPKM.subset <- log.tdata.FPKM.subset %>% rownames_to_column() %>% filter(rowname != "A113") %>% column_to_rownames()

log.tdata.FPKM.sample.info.subset.kidney <- log.tdata.FPKM.sample.info %>% rownames_to_column() %>% filter(Tissue == "Kidney") %>% column_to_rownames()

log.tdata.FPKM.subset <- subset(log.tdata.FPKM.sample.info.subset.kidney, select = -c(Time,Treatment,Tissue))
  
WGCNA.pathway <-readRDS(here("Data","Kidney","Chang_B6_96hr_4wk_gprofiler_pathway_annotation_list_kidney_WGCNA.RData"))

Matched<-readRDS(here("Data","Kidney","Annotated_genes_in_kidney_WGCNA_Chang_B6_96hr_4wk.RData"))


module.names <- Matched$X..Module.
name <- str_split(module.names,"_")
samples <-c()
for(i in 1:length(name)){
samples[[i]] <- name[[i]][2]
}  
name <- str_split(samples,"\"")
name <- unlist(name)

Treatment <- unclass(as.factor(log.tdata.FPKM.sample.info.subset.kidney[,27238]))
Time <- unclass(as.factor(log.tdata.FPKM.sample.info.subset.kidney[,27237]))
Treat.Time <- paste0(Treatment, Time)
phenotype <- data.frame(cbind(Treatment, Time, Treat.Time))

nSamples <- nrow(log.tdata.FPKM.sample.info.subset.kidney)

MEs0 <- read.csv(here("Data","Kidney","log.tdata.FPKM.sample.info.subset.kidney.WGCNA.module.eigens.csv"),header = T, row.names = 1)
name <- str_split(names(MEs0),"_")
samples <-c()
for(i in 1:length(name)){
samples[[i]] <- name[[i]][2]
}  
name <- str_split(samples,"\"")
name <- unlist(name)
colnames(MEs0) <-name
MEs <- orderMEs(MEs0)
moduleTraitCor <- cor(MEs, phenotype, use = "p");
moduleTraitPvalue <- corPvalueStudent(moduleTraitCor, nSamples)
```

## Relationship between Modules and Traits
```{r, results='asis'}
#sizeGrWindow(10,6)
# Will display correlations and their p-values
textMatrix = paste(signif(moduleTraitCor, 2), "\n(",
                        signif(moduleTraitPvalue, 1), ")", sep = "");
dim(textMatrix) = dim(moduleTraitCor)

# Display the correlation values within a heatmap plot
heat <- pheatmap(moduleTraitCor, main = paste("Module-trait relationships"), display_numbers = textMatrix,color=colorRampPalette(brewer.pal(n = 11, name = "Paired"))(10), cluster_rows = F, cluster_cols = F, fontsize_number = 4, angle_col = 45, number_color = "black", border_color = "white")
heat
```

## Top 10 Hub genes within each significant module {.tabset .tabset-fade .tabset-pills}
### Treatment

The top 10 genes that were significant for treatment within the **lightyellow** module and had the highest correlation with lightyellow were:

1. Grin3b
2. ENSMUSG00000081674
3. ENSMUSG00000094749
4. ENSMUSG00000084896
5. Gm15797
6. Wfikkn2
7. Iscu
8. ENSMUSG00000075589
9. C1qtfn6
10. Spink4

When assessing the overall sample contribution through their summary eigengenes it appears that for **lightyellow** all mice had a negative effect with the exception of one 4 wk control and one 96 hr control. All samples with a negative effect had mostly under-expressed genes while the two positive samples had mostly over-expressed genes.

The top 10 genes that were significant for treatment within the **purple** module and had the highest correlation with purple were:

1. Fam57a
2. ENSMUSG00000021944
3. ENSMUSG00000095547
4. ENSMUSG00000084132
5. Rfc4
6. Pcdhb3
7. Scnm1
8. Grik4
9. ENSMUSG00000074650
10. Nrn1l

When assessing the overall sample contribution through their summary eigengenes it appears that for **purple** all mice had a negative effect with the exception of two 4 wk 2DG and two 96 hr 2DG. All samples with a negative effect had mostly under-expressed genes while the 4 positive samples had mostly over-expressed genes.

The top 10 genes that were significant for treatment within the **lightcyan** module and had the highest correlation with lightcyan were:

1. Wnt6
2. ENSMUSG00000089667
3. Rps29
4. Mrpl11
5. Ndufa1
6. Rft1
7. Bccip
8. Atox1
9. Gm10241
10. Gm5834

When assessing the overall sample contribution through their summary eigengenes it appears that for **lightcyan** controls mostly had a negative effect while 2DG had a positive effect. Controls had mostly under-expressed genes while 2DG had mostly over-expressed genes.

### Time

The top 10 genes that were significant for time within the **blue** module and had the highest correlation with blue were:

1. Tnfrsf21
2. Rec8
3. Iws1
4. Ing1
5. Syt15
6. Slc25a35
7. Zfp652
8. Eya2
9. Abcc10
10. Pcgf6

When assessing the overall sample contribution through their summary eigengenes it appears that for **blue** controls mostly had a negative effect while 2DG had a half positive and half negative effect. Controls had mostly under-expressed genes while 2DG had both over and under-expressed genes.

The top 10 genes that were significant for time within the **pink** module and had the highest correlation with pink were:

1. ENSMUSG00000091393
2. Tmc8
3. Mmd
4. Rab27a
5. Adamts2
6. Gm26590
7. ENSMUSG00000059864
8. ENSMUSG00000070426
9. Hmox2
10. ENSMUSG00000086944

When assessing the overall sample contribution through their summary eigengenes it appears that for **pink** controls and 2DG mostly had a negative effect. 96 hr 2DG had mostly a positive effect. Controls and 2DG had mostly under-expressed genes while 96 hr 2DG samples had mostly over-expressed genes.

The top 10 genes that were significant for time within the **lightcyan** module and had the highest correlation with lightcyan were:

1. Chka
2. Mrpl30
3. ENSMUSG00000074354
4. Klf5
5. Ddx17
6. ENSMUSG00000092459
7. 9830147E19Rik
8. Car5b
9. Atox1
10. ENSMUSG00000054988

When assessing the overall sample contribution through their summary eigengenes it appears that for **lightcyan** controls mostly had a negative effect while 2DG had a positive effect, somewhat independent of time. Controls had mostly under-expressed genes while 2DG had mostly over-expressed genes.

The top 10 genes that were significant for time within the **midnightblue** module and had the highest correlation with midnightblue were:

1. Noc3l
2. Gm26588
3. Rtel1
4. Zfp189
5. Ppp1cb
6. Noxo1
7. Cd37
8. Zfp191
9. Anp32e
10. Ttc30b

When assessing the overall sample contribution through their summary eigengenes it appears that for **midnightblue** controls mostly had a negative effect while 4 wk 2DG had a negative effect and 96 hr 2DG had a positive effect. Controls had mostly under-expressed genes while 4wk 2DG had mostly under-expressed genes and 96 hr 2DG had mostly over-expressed genes.

### Treatment by time

The top 10 genes that were significant for treatment by time within the **lightyellow** module and had the highest correlation with lightyellow were:

1. Grin3b
2. ENSMUSG00000081674
3. ENSMUSG00000084896
4. Gm15797
5. Wfikkn2
6. ENSMUSG00000086918
7. Iscu
8. Pbk
9. ENSMUSG00000027077
10. C1qtnf6

When assessing the overall sample contribution through their summary eigengenes it appears that for **lightyellow** all mice had a negative effect with the exception of one 4 wk control and one 96 hr control. All samples with a negative effect had mostly under-expressed genes while the two positive samples had mostly over-expressed genes.

The top 10 genes that were significant for treatment by time within the **purple** module and had the highest correlation with purple were:

1. Fam57a
2. Trnp1
3. AV099323
4. 4930447C04Rik
5. ENSMUSG00000021944
6. ENSMUSG00000095547
7. ENSMUSG00000084132
8. Lcat
9. Mup10
10. Abca1

When assessing the overall sample contribution through their summary eigengenes it appears that for **purple** all mice had a negative effect with the exception of two 4 wk 2DG and two 96 hr 2DG. All samples with a negative effect had mostly under-expressed genes while the 4 positive samples had mostly over-expressed genes.

The top 10 genes that were significant for treatment by time within the **lightcyan** module and had the highest correlation with lightcyan were:

1. Gm561
2. Wnt6
3. ENSMUSG00000089667
4. Rps29
5. Mrpl11
6. Ndufa1
7. Zfc3h1
8. Rft1
9. Atox1
10. Fam136a

When assessing the overall sample contribution through their summary eigengenes it appears that for **lightcyan** controls mostly had a negative effect while 2DG had a positive effect, somewhat independent of time. Controls had mostly under-expressed genes while 2DG had mostly over-expressed genes.
