---
title: "Eigenmetabolite Stratification Prefrontal Cortex"
author: Ann Wells
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
   keep_md: TRUE
   code_folding: hide
   collapsed: no
   toc: yes
   toc_float: yes
   self_contained: no
   
---

# Introduction and Data files

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
options(stringsAsFactors = F)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(progress=FALSE)
```

This dataset contains nine tissues (heart, hippocampus, hypothalamus, kidney, liver, prefrontal cortex, skeletal muscle, small intestine, and spleen) from C57BL/6J mice that were fed 2-deoxyglucose (6g/L) through their drinking water for 96hrs or 4wks. 96hr mice were given their 2DG treatment 2 weeks after the other cohort started the 4 week treatment. The organs from the mice were harvested and processed for metabolomics and transcriptomics. The data in this document pertains to the transcriptomics data only. The counts that were used were FPKM normalized before being log transformed. It was determined that sample A113 had low RNAseq quality and through further analyses with PCA, MA plots, and clustering was an outlier and will be removed for the rest of the analyses performed. This document will determine the overall summary expression of each module across the main effects, as well as, assess the significance of each main effect and their interaction, using ANOVA, for each module and assess potential interactions visually for each module. 

```{r load packages}
needed.packages <- c("tidyverse", "here", "functional", "gplots", "dplyr", "GeneOverlap", "R.utils", "reshape2","magrittr","data.table", "RColorBrewer","preprocessCore", "ARTool","emmeans", "phia", "gProfileR", "WGCNA","plotly", "pheatmap","pander", "kableExtra")
for(i in 1:length(needed.packages)){library(needed.packages[i], character.only = TRUE)}

source(here("source_files","WGCNA_source.R"))
source(here("source_files","plot_theme.R"))
```

```{r load data}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

log.tdata.FPKM.sample.info <- cbind(log.tdata.FPKM, tdata.FPKM.sample.info[,27238:27240])

log.tdata.FPKM.sample.info <- log.tdata.FPKM.sample.info %>% rownames_to_column() %>% filter(rowname != "A113") %>% column_to_rownames()

log.tdata.FPKM.subset <- log.tdata.FPKM[,colMeans(log.tdata.FPKM != 0) > 0.5] 

log.tdata.FPKM.sample.info.subset <- cbind(log.tdata.FPKM.subset,tdata.FPKM.sample.info[,27238:27240])
log.tdata.FPKM.sample.info.subset <- log.tdata.FPKM.sample.info.subset %>% rownames_to_column() %>% filter(rowname != "A113") %>% column_to_rownames()

log.tdata.FPKM.sample.info.subset.prefrontal.cortex <- log.tdata.FPKM.sample.info.subset %>% rownames_to_column() %>% filter(Tissue == "Pre-frontal Cortex") %>% column_to_rownames()

log.tdata.FPKM.sample.info.subset.prefrontal.cortex$Treatment[log.tdata.FPKM.sample.info.subset.prefrontal.cortex$Treatment=="None"] <- "Control"

log.tdata.FPKM.sample.info.subset.prefrontal.cortex <- cbind(log.tdata.FPKM.sample.info.subset.prefrontal.cortex, Time.Treatment = paste(log.tdata.FPKM.sample.info.subset.prefrontal.cortex$Time, log.tdata.FPKM.sample.info.subset.prefrontal.cortex$Treatment))

module.labels <- readRDS(here("Data","Prefrontal Cortex","log.tdata.FPKM.sample.info.subset.prefrontal.cortex.WGCNA.module.labels.RData"))
module.eigens <- readRDS(here("Data","Prefrontal Cortex","log.tdata.FPKM.sample.info.subset.prefrontal.cortex.WGCNA.module.eigens.RData"))
modules <- readRDS(here("Data","Prefrontal Cortex","log.tdata.FPKM.sample.info.subset.prefrontal.cortex.WGCNA.module.membership.RData"))
net.deg <- readRDS(here("Data","Prefrontal Cortex","Chang_2DG_BL6_connectivity_prefrontal_cortex.RData"))
ensembl.location <- readRDS(here("Data","Ensembl_gene_id_and_location.RData"))
```

## Eigengene Stratification {.tabset .tabset-fade .tabset-pills}

Eigengene were stratified by time and treatment. The heatmap is a matrix of the average eigengene value for each level of the trait.

```{r, results='asis', cache=TRUE}
factors <- c("Time","Treatment","Time.Treatment")
eigenmetabolite(factors,log.tdata.FPKM.sample.info.subset.prefrontal.cortex)
```

## ANOVA {.tabset .tabset-fade .tabset-pills}
An ANOVA using aligned rank transformation was performed for each module. The full model is y ~ time + treatment + time:treatment.

```{r, results='asis'}
# Three-Way ANOVA for each Eigenmetabolite
model.data = dplyr::bind_cols(module.eigens[rownames(log.tdata.FPKM.sample.info.subset.prefrontal.cortex),], log.tdata.FPKM.sample.info.subset.prefrontal.cortex[,c("Time","Treatment")])
model.data$Time <- as.factor(model.data$Time)
model.data$Treatment <- as.factor(model.data$Treatment)

final.anova <- list()
for (m in colnames(module.eigens)) {
  a <- art(data = model.data, model.data[,m] ~ Time*Treatment)
  model <- anova(a)
  adjust <- p.adjust(model$`Pr(>F)`, method = "BH")
  
  final.anova[[m]] <- cbind(model, adjust)
}
```

### Blanchedalmond Module
```{r}
DT.table(final.anova[[1]])
```

### Chocolate4 Module
```{r}
DT.table(final.anova[[2]])
```
### Black Module
```{r}
DT.table(final.anova[[3]])
```

### lightgoldenrod3 Module
```{r}
DT.table(final.anova[[4]])
```

### Darkolivegreen2 Module
```{r}
DT.table(final.anova[[5]])
```

### Aquamarine Module
```{r}
DT.table(final.anova[[6]])
```

### Bisque2 Module
```{r}
DT.table(final.anova[[7]])
```

### Darkolivegreen4 Module
```{r}
DT.table(final.anova[[8]])
```

### Grey Module
```{r}
DT.table(final.anova[[9]])
```

### Blueviolet Module
```{r}
DT.table(final.anova[[10]])
```

### Darkturquoise Module
```{r}
DT.table(final.anova[[11]])
```

### Khaki3 Module
```{r}
DT.table(final.anova[[12]])
```

### Dodgerblue4 Module
```{r}
DT.table(final.anova[[13]])
```

### Cornsilk2 Module
```{r}
DT.table(final.anova[[14]])
```

### Darkseagreen4 Module
```{r}
DT.table(final.anova[[15]])
```

### Lightpink1 Module
```{r}
DT.table(final.anova[[16]])
```

### Navajowhite3 Module
```{r}
DT.table(final.anova[[17]])
```

### Antiquewhite Module
```{r}
DT.table(final.anova[[18]])
```

### Pink Module
```{r}
DT.table(final.anova[[19]])
```

### Salmon Module
```{r}
DT.table(final.anova[[20]])
```

### Lavenderblush2 Module
```{r}
DT.table(final.anova[[21]])
```

### Plum Module
```{r}
DT.table(final.anova[[22]])
```

### Goldenrod3 Module
```{r}
DT.table(final.anova[[23]])
```

### Chocolate2 Module
```{r}
DT.table(final.anova[[24]])
```

### Blue4 Module
```{r}
DT.table(final.anova[[25]])
```

### Mistyrose Module
```{r}
DT.table(final.anova[[26]])
```

### Cornsilk Module
```{r}
DT.table(final.anova[[27]])
```

### Lightskyblue2 Module
```{r}
DT.table(final.anova[[28]])
```

### Burlywood Module
```{r}
DT.table(final.anova[[29]])
```

### Oldlace Module
```{r}
DT.table(final.anova[[30]])
```

### Lightblue Module
```{r}
DT.table(final.anova[[31]])
```

### Limegreen Module
```{r}
DT.table(final.anova[[32]])
```

### Hotpink3 Module
```{r}
DT.table(final.anova[[33]])
```

### Lightskyblue Module
```{r}
DT.table(final.anova[[34]])
```

### Mediumorchid1 Module
```{r}
DT.table(final.anova[[35]])
```

### Rosybrown2 Module
```{r}
DT.table(final.anova[[36]])
```

## Interaction plots {.tabset .tabset-fade .tabset-pills}
Interaction plots were created to identify which modules have a potential interaction between time and treatment. A potential interaction is identified when the two lines cross.

```{r,results='asis', cache=TRUE}
for (m in module.labels) {
  p = plot.interaction(model.data, "Time", "Treatment", resp = m)
  name <- sapply(str_split(m,"_"),"[",2)
  cat("\n###",name,"\n")
  print(p)
  cat("\n \n")
}
```
