---
title: "Eigenmetabolite Stratification Small Intestine"
author: Ann Wells
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
   keep_md: TRUE
   code_folding: hide
   collapsed: no
   toc: yes
   toc_float: yes
   self_contained: no
   
---

# Introduction and Data files

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
options(stringsAsFactors = F)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(progress=FALSE)
```

This dataset contains nine tissues (heart, hippocampus, hypothalamus, kidney, liver, prefrontal cortex, skeletal muscle, small intestine, and spleen) from C57BL/6J mice that were fed 2-deoxyglucose (6g/L) through their drinking water for 96hrs or 4wks. 96hr mice were given their 2DG treatment 2 weeks after the other cohort started the 4 week treatment. The organs from the mice were harvested and processed for metabolomics and transcriptomics. The data in this document pertains to the transcriptomics data only. The counts that were used were FPKM normalized before being log transformed. It was determined that sample A113 had low RNAseq quality and through further analyses with PCA, MA plots, and clustering was an outlier and will be removed for the rest of the analyses performed. This document will determine the overall summary expression of each module across the main effects, as well as, assess the significance of each main effect and their interaction, using ANOVA, for each module and assess potential interactions visually for each module. 

```{r load packages}
needed.packages <- c("tidyverse", "here", "functional", "gplots", "dplyr", "GeneOverlap", "R.utils", "reshape2","magrittr","data.table", "RColorBrewer","preprocessCore", "ARTool","emmeans", "phia", "gProfileR", "WGCNA","plotly", "pheatmap","pander", "kableExtra")
for(i in 1:length(needed.packages)){library(needed.packages[i], character.only = TRUE)}

source(here("source_files","WGCNA_source.R"))
source(here("source_files","plot_theme.R"))
```

```{r load data}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

log.tdata.FPKM.sample.info <- cbind(log.tdata.FPKM, tdata.FPKM.sample.info[,27238:27240])

log.tdata.FPKM.sample.info <- log.tdata.FPKM.sample.info %>% rownames_to_column() %>% filter(rowname != "A113") %>% column_to_rownames()

log.tdata.FPKM.subset <- log.tdata.FPKM[,colMeans(log.tdata.FPKM != 0) > 0.5] 

log.tdata.FPKM.sample.info.subset <- cbind(log.tdata.FPKM.subset,tdata.FPKM.sample.info[,27238:27240])
log.tdata.FPKM.sample.info.subset <- log.tdata.FPKM.sample.info.subset %>% rownames_to_column() %>% filter(rowname != "A113") %>% column_to_rownames()

log.tdata.FPKM.sample.info.subset.small.intestine <- log.tdata.FPKM.sample.info.subset %>% rownames_to_column() %>% filter(Tissue == "Small Intestine") %>% column_to_rownames()

log.tdata.FPKM.sample.info.subset.small.intestine$Treatment[log.tdata.FPKM.sample.info.subset.small.intestine$Treatment=="None"] <- "Control"

log.tdata.FPKM.sample.info.subset.small.intestine <- cbind(log.tdata.FPKM.sample.info.subset.small.intestine, Time.Treatment = paste(log.tdata.FPKM.sample.info.subset.small.intestine$Time, log.tdata.FPKM.sample.info.subset.small.intestine$Treatment))

module.labels <- readRDS(here("Data","Small Intestine","log.tdata.FPKM.sample.info.subset.small.intestine.WGCNA.module.labels.RData"))
module.eigens <- readRDS(here("Data","Small Intestine","log.tdata.FPKM.sample.info.subset.small.intestine.WGCNA.module.eigens.RData"))
modules <- readRDS(here("Data","Small Intestine","log.tdata.FPKM.sample.info.subset.small.intestine.WGCNA.module.membership.RData"))
net.deg <- readRDS(here("Data","Small Intestine","Chang_2DG_BL6_connectivity_small_intestine.RData"))
ensembl.location <- readRDS(here("Data","Ensembl_gene_id_and_location.RData"))
```

## Eigengene Stratification {.tabset .tabset-fade .tabset-pills}

Eigengene were stratified by time and treatment. The heatmap is a matrix of the average eigengene value for each level of the trait.

```{r, results='asis', cache=TRUE}
factors <- c("Time","Treatment","Time.Treatment")
eigenmetabolite(factors,log.tdata.FPKM.sample.info.subset.small.intestine)
```

## ANOVA {.tabset .tabset-fade .tabset-pills}
An ANOVA using aligned rank transformation was performed for each module. The full model is y ~ time + treatment + time:treatment.

```{r, results='asis'}
# Three-Way ANOVA for each Eigenmetabolite
model.data = dplyr::bind_cols(module.eigens[rownames(log.tdata.FPKM.sample.info.subset.small.intestine),], log.tdata.FPKM.sample.info.subset.small.intestine[,c("Time","Treatment")])
model.data$Time <- as.factor(model.data$Time)
model.data$Treatment <- as.factor(model.data$Treatment)

final.anova <- list()
for (m in colnames(module.eigens)) {
  a <- art(data = model.data, model.data[,m] ~ Time*Treatment)
  model <- anova(a)
  adjust <- p.adjust(model$`Pr(>F)`, method = "BH")
  
  final.anova[[m]] <- cbind(model, adjust)
}
```

### Cornsilk Module
```{r}
DT.table(final.anova[[1]])
```

### Blue1 Module
```{r}
DT.table(final.anova[[2]])
```

### Rosybrown3 Module
```{r}
DT.table(final.anova[[3]])
```

### Antiquewhite2 Module
```{r}
DT.table(final.anova[[4]])
```

### Aliceblue Module
```{r}
DT.table(final.anova[[5]])
```

### Blue3 Module
```{r}
DT.table(final.anova[[6]])
```

### Coral1 Module
```{r}
DT.table(final.anova[[7]])
```

### Magenta3 Module
```{r}
DT.table(final.anova[[8]])
```

### Burlywood Module
```{r}
DT.table(final.anova[[9]])
```

### Lightblue2 Module
```{r}
DT.table(final.anova[[10]])
```

### Green4 Module
```{r}
DT.table(final.anova[[11]])
```

### Antiquewhite1 Module
```{r}
DT.table(final.anova[[12]])
```

### Sienna3 Module
```{r}
DT.table(final.anova[[13]])
```

### Coral4 Module
```{r}
DT.table(final.anova[[14]])
```

### Blue2 Module
```{r}
DT.table(final.anova[[15]])
```

### Antiquewhite4 Module
```{r}
DT.table(final.anova[[16]])
```

### Firebrick Module
```{r}
DT.table(final.anova[[17]])
```

### Deepskyblue Module
```{r}
DT.table(final.anova[[18]])
```

### Hotpink4 Module
```{r}
DT.table(final.anova[[19]])
```

### Grey Module
```{r}
DT.table(final.anova[[20]])
```

### Lightgreen Module
```{r}
DT.table(final.anova[[21]])
```

### Rosybrown4 Module
```{r}
DT.table(final.anova[[22]])
```

### Royalblue Module
```{r}
DT.table(final.anova[[23]])
```

### Orange Module
```{r}
DT.table(final.anova[[24]])
```

### White Module
```{r}
DT.table(final.anova[[25]])
```

### Slateblue2 Module
```{r}
DT.table(final.anova[[26]])
```

### Magenta2 Module
```{r}
DT.table(final.anova[[27]])
```

### Mediumpurple3 Module
```{r}
DT.table(final.anova[[28]])
```

### Thistle2 Module
```{r}
DT.table(final.anova[[29]])
```

### Yellow4 Module
```{r}
DT.table(final.anova[[30]])
```

### Indianred Module
```{r}
DT.table(final.anova[[31]])
```

### Antiquewhite Module
```{r}
DT.table(final.anova[[32]])
```

### Mediumpurple1 Module
```{r}
DT.table(final.anova[[33]])
```

### Lightblue4 Module
```{r}
DT.table(final.anova[[34]])
```

### Firebrick3 Module
```{r}
DT.table(final.anova[[35]])
```

### Mistyrose Module
```{r}
DT.table(final.anova[[36]])
```

### Moccasin Module
```{r}
DT.table(final.anova[[37]])
```

### Chocolate3 Module
```{r}
DT.table(final.anova[[38]])
```

### Pink2 Module
```{r}
DT.table(final.anova[[39]])
```

### Sienna1 Module
```{r}
DT.table(final.anova[[40]])
```

### Darkgoldenrod4 Module
```{r}
DT.table(final.anova[[41]])
```

### Lightskyblue2 Module
```{r}
DT.table(final.anova[[42]])
```

### Linen Module
```{r}
DT.table(final.anova[[43]])
```

### Oldlace Module
```{r}
DT.table(final.anova[[44]])
```

### Lightblue Module
```{r}
DT.table(final.anova[[45]])
```

### Red4 Module
```{r}
DT.table(final.anova[[46]])
```

## Interaction plots {.tabset .tabset-fade .tabset-pills}
Interaction plots were created to identify which modules have a potential interaction between time and treatment. A potential interaction is identified when the two lines cross.

```{r,results='asis', cache=TRUE}
for (m in module.labels) {
  p = plot.interaction(model.data, "Time", "Treatment", resp = m)
  name <- sapply(str_split(m,"_"),"[",2)
  cat("\n###",name,"\n")
  print(p)
  cat("\n \n")
}
```
