---
title: "Eigenmetabolite Stratification Brain"
author: Ann Wells
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
   keep_md: TRUE
   code_folding: hide
   collapsed: no
   toc: yes
   toc_float: yes
   self_contained: no
   
---

# Introduction and Data files

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
options(stringsAsFactors = F)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(progress=FALSE)
```

This dataset contains nine tissues (heart, hippocampus, hypothalamus, kidney, liver, prefrontal cortex, skeletal muscle, small intestine, and spleen) from C57BL/6J mice that were fed 2-deoxyglucose (6g/L) through their drinking water for 96hrs or 4wks. 96hr mice were given their 2DG treatment 2 weeks after the other cohort started the 4 week treatment. The organs from the mice were harvested and processed for metabolomics and transcriptomics. The data in this document pertains to the transcriptomics data only. The counts that were used were FPKM normalized before being log transformed. It was determined that sample A113 had low RNAseq quality and through further analyses with PCA, MA plots, and clustering was an outlier and will be removed for the rest of the analyses performed. This document will determine the overall summary expression of each module across the main effects, as well as, assess the significance of each main effect and their interaction, using ANOVA, for each module and assess potential interactions visually for each module. 

```{r load packages}
needed.packages <- c("tidyverse", "here", "functional", "gplots", "dplyr", "GeneOverlap", "R.utils", "reshape2","magrittr","data.table", "RColorBrewer","preprocessCore", "ARTool","emmeans", "phia", "gProfileR", "WGCNA","plotly", "pheatmap","pander", "kableExtra")
for(i in 1:length(needed.packages)){library(needed.packages[i], character.only = TRUE)}

source(here("source_files","WGCNA_source.R"))
source(here("source_files","plot_theme.R"))
```

```{r load data}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

log.tdata.FPKM.sample.info <- cbind(log.tdata.FPKM, tdata.FPKM.sample.info[,27238:27240])

log.tdata.FPKM.sample.info <- log.tdata.FPKM.sample.info %>% rownames_to_column() %>% filter(rowname != "A113") %>% column_to_rownames()

log.tdata.FPKM.subset <- log.tdata.FPKM[,colMeans(log.tdata.FPKM != 0) > 0.5] 

log.tdata.FPKM.sample.info.subset <- cbind(log.tdata.FPKM.subset,tdata.FPKM.sample.info[,27238:27240])
log.tdata.FPKM.sample.info.subset <- log.tdata.FPKM.sample.info.subset %>% rownames_to_column() %>% filter(rowname != "A113") %>% column_to_rownames()


log.tdata.FPKM.sample.info.subset.hip.hyp.cortex <- log.tdata.FPKM.sample.info.subset %>% rownames_to_column() %>% 
  filter(Tissue %in% c("Pre-frontal Cortex","Hippocampus","Hypothanamus")) %>% 
  column_to_rownames()

log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Treatment[log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Treatment=="None"] <- "Control"

log.tdata.FPKM.sample.info.subset.hip.hyp.cortex <- cbind(log.tdata.FPKM.sample.info.subset.hip.hyp.cortex, Time.Treatment = paste(log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Time,log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Treatment), Time.Tissue = paste(log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Time,log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Tissue), Tissue.Treatment = paste(log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Tissue,log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Treatment), Time.Treatment.Tissue = paste(log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Time, log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Treatment,log.tdata.FPKM.sample.info.subset.hip.hyp.cortex$Tissue))

module.labels <- readRDS(here("Data","Brain","log.tdata.FPKM.sample.info.subset.hip.hyp.cortex.WGCNA.module.labels.RData"))
module.eigens <- readRDS(here("Data","Brain","log.tdata.FPKM.sample.info.subset.hip.hyp.cortex.WGCNA.module.eigens.RData"))
modules <- readRDS(here("Data","Brain","log.tdata.FPKM.sample.info.subset.hip.hyp.cortex.WGCNA.module.membership.RData"))
net.deg <- readRDS(here("Data","Brain","Chang_2DG_BL6_connectivity_hip_hyp_cortex.RData"))
ensembl.location <- readRDS(here("Data","Ensembl_gene_id_and_location.RData"))
```

## Eigengene Stratification {.tabset .tabset-fade .tabset-pills}

Eigengene were stratified by time and treatment. The heatmap is a matrix of the average eigengene value for each level of the trait.

```{r, results='asis', cache=TRUE}
factors <- c("Time","Treatment","Tissue","Time.Treatment","Time.Tissue","Tissue.Treatment","Time.Treatment.Tissue")
eigenmetabolite(factors,log.tdata.FPKM.sample.info.subset.hip.hyp.cortex)
```

## ANOVA {.tabset .tabset-fade .tabset-pills}
An ANOVA was performed for each module. The full model is y ~ time + treatment + time:treatment.

```{r, results='asis'}
# Three-Way ANOVA for each Eigenmetabolite
model.data = dplyr::bind_cols(module.eigens[rownames(log.tdata.FPKM.sample.info.subset.hip.hyp.cortex),], log.tdata.FPKM.sample.info.subset.hip.hyp.cortex[,c("Time","Treatment","Tissue")])
model.data$Time <- as.factor(model.data$Time)
model.data$Tissue <- as.factor(model.data$Tissue)
model.data$Treatment <- as.factor(model.data$Treatment)

final.anova <- list()
for (m in colnames(module.eigens)) {
  a <- art(data = model.data, model.data[,m] ~ Time*Treatment*Tissue)
  model <- anova(a)
  adjust <- p.adjust(model$`Pr(>F)`, method = "BH")
  
  name <- sapply(str_split(colnames(module.eigens[m]),"_"),"[",2)
  
  final.anova[[m]] <- cbind(model, adjust)
}
```

### Antiquewhite Module
```{r}
DT.table(final.anova[[1]])
```

### Cyan Module
```{r}
DT.table(final.anova[[2]])
```

### Lavenderblush1 Module
```{r}
DT.table(final.anova[[3]])
```

### Darkolivegreen4 Module
```{r}
DT.table(final.anova[[4]])
```

### Darkgrey Module
```{r}
DT.table(final.anova[[5]])
```

### Brown3 Module
```{r}
DT.table(final.anova[[6]])
```

### Orangered1 Module
```{r}
DT.table(final.anova[[7]])
```

### Deeppink2 Module
```{r}
DT.table(final.anova[[8]])
```

### Grey Module
```{r}
DT.table(final.anova[[9]])
```

### Magenta1 Module
```{r}
DT.table(final.anova[[10]])
```

### Mediumpurple Module
```{r}
DT.table(final.anova[[11]])
```

### Darkslateblue Module
```{r}
DT.table(final.anova[[12]])
```

### Magenta4 Module
```{r}
DT.table(final.anova[[13]])
```

### Firebrick4 Module
```{r}
DT.table(final.anova[[14]])
```

### Honeydew Module
```{r}
DT.table(final.anova[[15]])
```

### Brown1 Module
```{r}
DT.table(final.anova[[16]])
```

### Coral3 Module
```{r}
DT.table(final.anova[[17]])
```

### Royalblue Module
```{r}
DT.table(final.anova[[18]])
```

### Green3 Module
```{r}
DT.table(final.anova[[19]])
```

### Lavenderblush3 Module
```{r}
DT.table(final.anova[[20]])
```

### Green4 Module
```{r}
DT.table(final.anova[[21]])
```

### Lightblue1 Module
```{r}
DT.table(final.anova[[22]])
```

### Magenta3 Module
```{r}
DT.table(final.anova[[23]])
```

### Blanchedalmond Module
```{r}
DT.table(final.anova[[24]])
```

### Orangered4 Module
```{r}
DT.table(final.anova[[25]])
```

### Darkseagreen Module
```{r}
DT.table(final.anova[[26]])
```

### Paleturquoise4 Module
```{r}
DT.table(final.anova[[27]])
```

### Chocolate3 Module
```{r}
DT.table(final.anova[[28]])
```

### Indianred3 Module
```{r}
DT.table(final.anova[[29]])
```

### Plum Module
```{r}
DT.table(final.anova[[30]])
```

### Lightcoral Module
```{r}
DT.table(final.anova[[31]])
```

### Aliceblue Module
```{r}
DT.table(final.anova[[32]])
```

### Burlywood Module
```{r}
DT.table(final.anova[[33]])
```

### Thistle3 Module
```{r}
DT.table(final.anova[[34]])
```

### Lavenderblush2 Module
```{r}
DT.table(final.anova[[35]])
```

### Pink2 Module
```{r}
DT.table(final.anova[[36]])
```

### Lightblue2 Module
```{r}
DT.table(final.anova[[37]])
```

### Wheat3 Module
```{r}
DT.table(final.anova[[38]])
```

### Mediumorchid3 Module
```{r}
DT.table(final.anova[[39]])
```

### Orange3 Module
```{r}
DT.table(final.anova[[40]])
```

### Dodgerblue4 Module
```{r}
DT.table(final.anova[[41]])
```

## Interaction plots {.tabset .tabset-fade .tabset-pills}
Interaction plots were created to identify which modules have a potential interaction between time and treatment. A potential interaction is identified when the two lines cross.

```{r,results='asis', cache=TRUE}
for (m in module.labels) {
  p = plot.interaction(model.data, "Time", "Treatment","Tissue", resp = m)
  name <- sapply(str_split(m,"_"),"[",2)
  cat("\n###",name,"\n")
  print(p)
  cat("\n \n")
}
```
