---
title: "Chang_B6_96hr_4wk 2DG Scatterplots Across Tissue Modules for Chosen Modules"
author: Ann Wells
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
   keep_md: TRUE
   code_folding: hide
   collapsed: no
   toc: yes
   toc_float: yes
   self_contained: no
   
---

# Introduction

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
options(stringsAsFactors = F)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(progress=FALSE)

```

This dataset contains nine tissues (heart, hippocampus, hypothalamus, kidney, liver, prefrontal cortex, skeletal muscle, small intestine, and spleen) from C57BL6/J mice that were fed 2-deoxyglucose (6g/L) through their drinking water for 96hrs or 4wks. 96hr mice were given their 2DG treatment 2 weeks after the other cohort started the 4 week treatment. The organs from the mice were harvested and processed for metabolomics and transcriptomics. The data in this document pertains to the transcriptomics data only. The counts that were used were FPKM normalized before being log transformed. It was determined that sample A113 had low RNAseq quality and through further analyses with PCA, MA plots, and clustering was an outlier and will be removed for the rest of the analyses performed. This document will plot correlations of GSVA eigengenes for each pathway across tissues of interest.

```{r load packages}
needed.packages <- c("tidyverse", "here", "functional", "gplots", "dplyr", "GeneOverlap", "R.utils", "reshape2","magrittr","data.table", "RColorBrewer","preprocessCore", "ARTool","emmeans", "phia", "gprofiler2","rlist", "plotly","kableExtra","foreach","doParallel","doFuture","pheatmap")
for(i in 1:length(needed.packages)){library(needed.packages[i], character.only = TRUE)}

source(here("source_files","WGCNA_source.R"))
```

```{r load initial data}
heart <- readRDS(here("Data","Heart","log.tdata.FPKM.sample.info.subset.heart.WGCNA.module.eigens.RData"))

hypothalamus <- readRDS(here("Data","Hypothalamus","log.tdata.FPKM.sample.info.subset.hypothalamus.WGCNA.module.eigens.RData"))

liver <- readRDS(here("Data","Liver","log.tdata.FPKM.sample.info.subset.liver.WGCNA.module.eigens.RData"))

prefrontal.cortex <- readRDS(here("Data","Prefrontal Cortex","log.tdata.FPKM.sample.info.subset.prefrontal.cortex.WGCNA.module.eigens.RData"))

skeletal.muscle <- readRDS(here("Data","Skeletal Muscle","log.tdata.FPKM.sample.info.subset.skeletal.muscle.WGCNA.module.eigens.RData"))

small.intestine <- readRDS(here("Data","Small Intestine", "log.tdata.FPKM.sample.info.subset.small.intestine.WGCNA.module.eigens.RData"))

```

```{r relabel columns for files}
## heart
modulenames <- c()
  for(i in 1:length(heart)){
    name <- strsplit(colnames(heart),"_")
    modulenames[i] <- name[[i]][2]
  }

colnames(heart) <- modulenames

## hypothalamus
modulenames <- c()
  for(i in 1:length(hypothalamus)){
    name <- strsplit(colnames(hypothalamus),"_")
    modulenames[i] <- name[[i]][2]
  }

colnames(hypothalamus) <- modulenames

## liver
modulenames <- c()
  for(i in 1:length(liver)){
    name <- strsplit(colnames(liver),"_")
    modulenames[i] <- name[[i]][2]
  }

colnames(liver) <- modulenames

## muscle
modulenames <- c()
  for(i in 1:length(skeletal.muscle)){
    name <- strsplit(colnames(skeletal.muscle),"_")
    modulenames[i] <- name[[i]][2]
  }

colnames(skeletal.muscle) <- modulenames

## prefrontal cortex
modulenames <- c()
  for(i in 1:length(prefrontal.cortex)){
    name <- strsplit(colnames(prefrontal.cortex),"_")
    modulenames[i] <- name[[i]][2]
  }

colnames(prefrontal.cortex) <- modulenames

## small intestine
modulenames <- c()
  for(i in 1:length(small.intestine)){
    name <- strsplit(colnames(small.intestine),"_")
    modulenames[i] <- name[[i]][2]
  }

names(small.intestine) <- modulenames

modules.sig <- cbind(heart$darkgreen, hypothalamus$bisque4, prefrontal.cortex$bisque2, small.intestine$green4, skeletal.muscle$salmon2, liver$darkolivegreen)
colnames(modules.sig) <- c("Heart","Hypothalamus", "Prefrontal Cortex","Small Intestine","Skeletal Muscle","Liver")
rownames(modules.sig) <- rownames(prefrontal.cortex)
```

```{r load data}
heart.gsva <- readRDS(here("Data","Heart","GSVA.modules.heart.RData"))
heart.pathways <- readRDS(here("Data","Heart","Chang_B6_96hr_4wk_gprofiler_pathway_annotation_list_heart_WGCNA.RData"))
term.names <- heart.pathways[[4]]$term_name
heart.darkgreen <- heart.gsva$log.tdata.FPKM.sample.info.subset.heart.WGCNA_darkgreen[,match(term.names,colnames(heart.gsva$log.tdata.FPKM.sample.info.subset.heart.WGCNA_darkgreen))]
heart.darkgreen <- heart.darkgreen[, colSums(is.na(heart.darkgreen)) != nrow(heart.darkgreen)]

hypothalamus.gsva <- readRDS(here("Data","Hypothalamus","GSVA.modules.hypothalamus.RData"))
hypothalamus.pathways <- readRDS(here("Data","Hypothalamus","Chang_B6_96hr_4wk_gprofiler_pathway_annotation_list_hypothalamus_WGCNA.RData"))
term.names <- hypothalamus.pathways[[3]]$term_name
hypothalamus.bisque4 <- hypothalamus.gsva$log.tdata.FPKM.sample.info.subset.hypothalamus.WGCNA_bisque4[,match(term.names,colnames(hypothalamus.gsva$log.tdata.FPKM.sample.info.subset.hypothalamus.WGCNA_bisque4))]
hypothalamus.bisque4 <- hypothalamus.bisque4[, colSums(is.na(hypothalamus.bisque4)) != nrow(hypothalamus.bisque4)]
  

liver.gsva <- readRDS(here("Data","Liver","GSVA.modules.liver.RData"))
liver.pathways <- readRDS(here("Data","Liver","Chang_B6_96hr_4wk_gprofiler_pathway_annotation_list_liver_WGCNA.RData"))
term.names <- liver.pathways[[8]]$term_name
liver.darkolivegreen <- liver.gsva$log.tdata.FPKM.sample.info.subset.liver.WGCNA_darkolivegreen[,match(term.names,colnames(liver.gsva$log.tdata.FPKM.sample.info.subset.liver.WGCNA_darkolivegreen))]

prefrontal.cortex.gsva <- readRDS(here("Data","Prefrontal Cortex","GSVA.modules.prefrontal.cortex.RData"))
prefrontal.cortex.pathways <- readRDS(here("Data","Prefrontal Cortex","Chang_B6_96hr_4wk_gprofiler_pathway_annotation_list_prefrontal_cortex_WGCNA.RData"))
term.names <- prefrontal.cortex.pathways[[3]]$term_name
prefrontal.cortex.bisque2 <- prefrontal.cortex.gsva$log.tdata.FPKM.sample.info.subset.prefrontal.cortex.WGCNA_bisque2[,match(term.names,colnames(prefrontal.cortex.gsva$log.tdata.FPKM.sample.info.subset.prefrontal.cortex.WGCNA_bisque2))]
prefrontal.cortex.bisque2 <- prefrontal.cortex.bisque2[, colSums(is.na(prefrontal.cortex.bisque2)) != nrow(prefrontal.cortex.bisque2)]

skeletal.muscle.gsva <- readRDS(here("Data","Skeletal Muscle","GSVA.modules.skeletal.muscle.RData"))
skeletal.muscle.pathways <- readRDS(here("Data","Skeletal Muscle","Chang_B6_96hr_4wk_gprofiler_pathway_annotation_list_skeletal_muscle_WGCNA.RData"))
term.names <- skeletal.muscle.pathways[[35]]$term_name
skeletal.muscle.salmon2 <- skeletal.muscle.gsva$log.tdata.FPKM.sample.info.subset.skeletal.muscle.WGCNA_salmon2[,match(term.names,colnames(skeletal.muscle.gsva$log.tdata.FPKM.sample.info.subset.skeletal.muscle.WGCNA_salmon2))]
skeletal.muscle.salmon2 <- skeletal.muscle.salmon2[, colSums(is.na(skeletal.muscle.salmon2)) != nrow(skeletal.muscle.salmon2)]

small.intestine.gsva <- readRDS(here("Data","Small Intestine","GSVA.modules.small.intestine.RData"))
small.intestine.pathways <- readRDS(here("Data","Small Intestine","Chang_B6_96hr_4wk_gprofiler_pathway_annotation_list_small_intestine_WGCNA.RData"))
term.names <- small.intestine.pathways[[18]]$term_name
small.intestine.green4 <- small.intestine.gsva$log.tdata.FPKM.sample.info.subset.small.intestine.WGCNA_green4[,match(term.names, colnames(small.intestine.gsva$log.tdata.FPKM.sample.info.subset.small.intestine.WGCNA_green4))]
small.intestine.green4 <- small.intestine.green4[, colSums(is.na(small.intestine.green4)) != nrow(small.intestine.green4)]

modules.tissue <- list(heart.darkgreen, hypothalamus.bisque4, prefrontal.cortex.bisque2, small.intestine.green4)

names(modules.tissue) <- c("heart.darkgreen", "hypothalamus.bisque4", "prefrontal.cortex.bisque2", "small.intestine.green4")
```

## Correlations {.tabset .tabset-fade .tabset-pills}

```{r corr loop, results='asis'}
for(i in 1:length(modules.tissue)){
  for(j in 1:length(modules.tissue)){
    cat("\n###",paste(names(modules.tissue[i]), "vs", names(modules.tissue[j])),"{.tabset .tabset-fade .tabset-pills}","\n")
    correlations <- cor(modules.tissue[[i]], modules.tissue[[j]])
    pheatmap(correlations, show_rownames = T,show_colnames = T, fontsize_col = 4, fontsize_row = 2, color = colorRampPalette(rev(brewer.pal(n = 9, name =
  "BuPu")))(100))
    cat("\n \n")
  }
}
```

```{r corr loop liver, results='asis'}
  for(j in 1:length(modules.tissue)){
    cat("\n###",paste("liver.darkolivegreen", "vs", names(modules.tissue[j])),"{.tabset .tabset-fade .tabset-pills}","\n")
    correlations <- cor(liver.darkolivegreen, modules.tissue[[j]])
    pheatmap(correlations, show_rownames = T,show_colnames = T, fontsize_col = 4, fontsize_row = 4, color = colorRampPalette(rev(brewer.pal(n = 9, name =
  "BuPu")))(100), cluster_rows = F)
    cat("\n \n")
  }

```

```{r corr}
# correlations <- cor(heart.darkgreen,small.intestine.green4)
# breaks <- seq(-.65,.61,length.out = 100)
# pdf("Heatmap of small intestine green4 and heart darkgreen correlations GSVA pathways.pdf")
# pheatmap(correlations, show_rownames = T,show_colnames = T, fontsize_col = 8, fontsize_row = 8, color = colorRampPalette(rev(brewer.pal(n = 11, name =
#   "Spectral")))(100), breaks = breaks)
# dev.off()
```