## Scree plot and summary statistics Spleen
```{r PCA spleen log 96hr}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM.sample.info.spleen <- rownames_to_column(tdata.FPKM.sample.info) %>% filter(Tissue=="Spleen" & Time=="96 hrs") %>% column_to_rownames('rowname')

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

rows <- rownames(tdata.FPKM.sample.info.spleen)

log.tdata.FPKM.spleen <- rownames_to_column(log.tdata.FPKM) 

log.tdata.FPKM.spleen <- log.tdata.FPKM.spleen %>% filter(rowname %in% rows) %>% column_to_rownames('rowname')

pca <- prcomp(log.tdata.FPKM.spleen, center = T)

screeplot(pca,type = "lines")

summary(pca)
```

## Treatment Spleen
```{r spleen log PCA Treatment 96hr}

Treatment_color <- as.factor(tdata.FPKM.sample.info.spleen$Treatment)
Treatment_color <- as.data.frame(Treatment_color)
col_treatment <- colorRampPalette(brewer.pal(n = 12, name = "Paired"))(2)[Treatment_color$Treatment_color]
pca_treatment <- cbind(Treatment_color,pca$x[,1],pca$x[,2])
pca_treatment <- as.data.frame(pca_treatment)

p <- ggplot(pca_treatment,aes(pca$x[,1], pca$x[,2]))
p <- p + geom_point(aes(fill = as.factor(pca_treatment$Treatment_color)), shape=21, size=4) + theme_bw()
p <- p + theme(legend.title = element_text(size=10,face="bold")) + 
  theme(legend.text = element_text(size=10, face="bold"))
p <- p + xlab("PCA 1 (33.6%)") + ylab("PCA 2 (25.22%)") + theme(axis.title = element_text(face="bold"))
p <- p + stat_ellipse(aes(pca$x[,1], pca$x[,2], group = Treatment_color, fill = as.factor(pca_treatment$Treatment_color)), geom="polygon",level=0.95,alpha=0.4) +
  scale_fill_manual(values=c("#A6CEE3", "#B15928"),name="Treatment Type",
                       breaks=c("2DG", "None"),
                       labels=c("2DG", "Control")) +
  scale_linetype_manual(values=c(1,2))
print(p)
```

## Scree plot and summary statistics kidney
```{r PCA kidney log 96hr}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM.sample.info.kidney <- rownames_to_column(tdata.FPKM.sample.info) %>% filter(Tissue=="Kidney" & Time=="96 hrs") %>% column_to_rownames('rowname')

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

rows <- rownames(tdata.FPKM.sample.info.kidney)

log.tdata.FPKM.kidney <- rownames_to_column(log.tdata.FPKM) 

log.tdata.FPKM.kidney <- log.tdata.FPKM.kidney %>% filter(rowname %in% rows) %>% column_to_rownames('rowname')

pca <- prcomp(log.tdata.FPKM.kidney, center = T)

screeplot(pca,type = "lines")

summary(pca)
```

## Treatment kidney
```{r kidney log PCA Treatment 96hr}

Treatment_color <- as.factor(tdata.FPKM.sample.info.kidney$Treatment)
Treatment_color <- as.data.frame(Treatment_color)
col_treatment <- colorRampPalette(brewer.pal(n = 12, name = "Paired"))(2)[Treatment_color$Treatment_color]
pca_treatment <- cbind(Treatment_color,pca$x[,1],pca$x[,2])
pca_treatment <- as.data.frame(pca_treatment)

p <- ggplot(pca_treatment,aes(pca$x[,1], pca$x[,2]))
p <- p + geom_point(aes(fill = as.factor(pca_treatment$Treatment_color)), shape=21, size=4) + theme_bw()
p <- p + theme(legend.title = element_text(size=10,face="bold")) + 
  theme(legend.text = element_text(size=10, face="bold"))
p <- p + xlab("PCA 1 (36.27%)") + ylab("PCA 2 (18.38%)") + theme(axis.title = element_text(face="bold"))
p <- p + stat_ellipse(aes(pca$x[,1], pca$x[,2], group = Treatment_color, fill = as.factor(pca_treatment$Treatment_color)), geom="polygon",level=0.95,alpha=0.4) +
  scale_fill_manual(values=c("#A6CEE3", "#B15928"),name="Treatment Type",
                       breaks=c("2DG", "None"),
                       labels=c("2DG", "Control")) +
  scale_linetype_manual(values=c(1,2))
print(p)
```

## Scree plot and summary statistics hypothalamus
```{r PCA hypothalamus log 96hr}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM.sample.info.hypothalamus <- rownames_to_column(tdata.FPKM.sample.info) %>% filter(Tissue=="Hypothanamus" & Time=="96 hrs") %>% column_to_rownames('rowname')

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

rows <- rownames(tdata.FPKM.sample.info.hypothalamus)

log.tdata.FPKM.hypothalamus <- rownames_to_column(log.tdata.FPKM) 

log.tdata.FPKM.hypothalamus <- log.tdata.FPKM.hypothalamus %>% filter(rowname %in% rows) %>% column_to_rownames('rowname')

pca <- prcomp(log.tdata.FPKM.hypothalamus, center = T)

screeplot(pca,type = "lines")

summary(pca)
```

## Treatment hypothalamus
```{r hypothalamus log PCA Treatment 96hr}

Treatment_color <- as.factor(tdata.FPKM.sample.info.hypothalamus$Treatment)
Treatment_color <- as.data.frame(Treatment_color)
col_treatment <- colorRampPalette(brewer.pal(n = 12, name = "Paired"))(2)[Treatment_color$Treatment_color]
pca_treatment <- cbind(Treatment_color,pca$x[,1],pca$x[,2])
pca_treatment <- as.data.frame(pca_treatment)

p <- ggplot(pca_treatment,aes(pca$x[,1], pca$x[,2]))
p <- p + geom_point(aes(fill = as.factor(pca_treatment$Treatment_color)), shape=21, size=4) + theme_bw()
p <- p + theme(legend.title = element_text(size=10,face="bold")) + 
  theme(legend.text = element_text(size=10, face="bold"))
p <- p + xlab("PCA 1 (30.25%)") + ylab("PCA 2 (23.83%)") + theme(axis.title = element_text(face="bold"))
p <- p + stat_ellipse(aes(pca$x[,1], pca$x[,2], group = Treatment_color, fill = as.factor(pca_treatment$Treatment_color)), geom="polygon",level=0.95,alpha=0.4) +
  scale_fill_manual(values=c("#A6CEE3", "#B15928"),name="Treatment Type",
                       breaks=c("2DG", "None"),
                       labels=c("2DG", "Control")) +
  scale_linetype_manual(values=c(1,2))
print(p)
```

## Scree plot and summary statistics hippocampus
```{r PCA hippocampus log 96hr}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM.sample.info.hippocampus <- rownames_to_column(tdata.FPKM.sample.info) %>% filter(Tissue=="Hippocampus" & Time=="96 hrs") %>% column_to_rownames('rowname')

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

rows <- rownames(tdata.FPKM.sample.info.hippocampus)

log.tdata.FPKM.hippocampus <- rownames_to_column(log.tdata.FPKM) 

log.tdata.FPKM.hippocampus <- log.tdata.FPKM.hippocampus %>% filter(rowname %in% rows) %>% column_to_rownames('rowname')

pca <- prcomp(log.tdata.FPKM.hippocampus, center = T)

screeplot(pca,type = "lines")

summary(pca)
```

## Treatment hippocampus
```{r hippocampus log PCA Treatment 96hr}

Treatment_color <- as.factor(tdata.FPKM.sample.info.hippocampus$Treatment)
Treatment_color <- as.data.frame(Treatment_color)
col_treatment <- colorRampPalette(brewer.pal(n = 12, name = "Paired"))(2)[Treatment_color$Treatment_color]
pca_treatment <- cbind(Treatment_color,pca$x[,1],pca$x[,2])
pca_treatment <- as.data.frame(pca_treatment)

p <- ggplot(pca_treatment,aes(pca$x[,1], pca$x[,2]))
p <- p + geom_point(aes(fill = as.factor(pca_treatment$Treatment_color)), shape=21, size=4) + theme_bw()
p <- p + theme(legend.title = element_text(size=10,face="bold")) + 
  theme(legend.text = element_text(size=10, face="bold"))
p <- p + xlab("PCA 1 (31.9%)") + ylab("PCA 2 (21.06%)") + theme(axis.title = element_text(face="bold"))
p <- p + stat_ellipse(aes(pca$x[,1], pca$x[,2], group = Treatment_color, fill = as.factor(pca_treatment$Treatment_color)), geom="polygon",level=0.95,alpha=0.4) +
  scale_fill_manual(values=c("#A6CEE3", "#B15928"),name="Treatment Type",
                       breaks=c("2DG", "None"),
                       labels=c("2DG", "Control")) +
  scale_linetype_manual(values=c(1,2))
print(p)
```

## Scree plot and summary statistics liver
```{r PCA liver log 96hr}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM.sample.info.liver <- rownames_to_column(tdata.FPKM.sample.info) %>% filter(Tissue=="Liver" & Time=="96 hrs") %>% column_to_rownames('rowname')

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

rows <- rownames(tdata.FPKM.sample.info.liver)

log.tdata.FPKM.liver <- rownames_to_column(log.tdata.FPKM) 

log.tdata.FPKM.liver <- log.tdata.FPKM.liver %>% filter(rowname %in% rows) %>% column_to_rownames('rowname')

pca <- prcomp(log.tdata.FPKM.liver, center = T)

screeplot(pca,type = "lines")

summary(pca)
```

## Treatment liver
```{r liver log PCA Treatment 96hr}

Treatment_color <- as.factor(tdata.FPKM.sample.info.liver$Treatment)
Treatment_color <- as.data.frame(Treatment_color)
col_treatment <- colorRampPalette(brewer.pal(n = 12, name = "Paired"))(2)[Treatment_color$Treatment_color]
pca_treatment <- cbind(Treatment_color,pca$x[,1],pca$x[,2])
pca_treatment <- as.data.frame(pca_treatment)

p <- ggplot(pca_treatment,aes(pca$x[,1], pca$x[,2]))
p <- p + geom_point(aes(fill = as.factor(pca_treatment$Treatment_color)), shape=21, size=4) + theme_bw()
p <- p + theme(legend.title = element_text(size=10,face="bold")) + 
  theme(legend.text = element_text(size=10, face="bold"))
p <- p + xlab("PCA 1 (32.81%)") + ylab("PCA 2 (20.38%)") + theme(axis.title = element_text(face="bold"))
p <- p + stat_ellipse(aes(pca$x[,1], pca$x[,2], group = Treatment_color, fill = as.factor(pca_treatment$Treatment_color)), geom="polygon",level=0.95,alpha=0.4) +
  scale_fill_manual(values=c("#A6CEE3", "#B15928"),name="Treatment Type",
                       breaks=c("2DG", "None"),
                       labels=c("2DG", "Control")) +
  scale_linetype_manual(values=c(1,2))
print(p)
```

## Scree plot and summary statistics heart
```{r PCA heart log 96hr}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM.sample.info.heart <- rownames_to_column(tdata.FPKM.sample.info) %>% filter(Tissue=="Heart" & Time=="96 hrs") %>% column_to_rownames('rowname')

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

rows <- rownames(tdata.FPKM.sample.info.heart)

log.tdata.FPKM.heart <- rownames_to_column(log.tdata.FPKM) 

log.tdata.FPKM.heart <- log.tdata.FPKM.heart %>% filter(rowname %in% rows) %>% column_to_rownames('rowname')

pca <- prcomp(log.tdata.FPKM.heart, center = T)

screeplot(pca,type = "lines")

summary(pca)
```

## Treatment heart
```{r heart log PCA Treatment 96hr}

Treatment_color <- as.factor(tdata.FPKM.sample.info.heart$Treatment)
Treatment_color <- as.data.frame(Treatment_color)
col_treatment <- colorRampPalette(brewer.pal(n = 12, name = "Paired"))(2)[Treatment_color$Treatment_color]
pca_treatment <- cbind(Treatment_color,pca$x[,1],pca$x[,2])
pca_treatment <- as.data.frame(pca_treatment)

p <- ggplot(pca_treatment,aes(pca$x[,1], pca$x[,2]))
p <- p + geom_point(aes(fill = as.factor(pca_treatment$Treatment_color)), shape=21, size=4) + theme_bw()
p <- p + theme(legend.title = element_text(size=10,face="bold")) + 
  theme(legend.text = element_text(size=10, face="bold"))
p <- p + xlab("PCA 1 (37.36%)") + ylab("PCA 2 (20.27%)") + theme(axis.title = element_text(face="bold"))
p <- p + stat_ellipse(aes(pca$x[,1], pca$x[,2], group = Treatment_color, fill = as.factor(pca_treatment$Treatment_color)), geom="polygon",level=0.95,alpha=0.4) +
  scale_fill_manual(values=c("#A6CEE3", "#B15928"),name="Treatment Type",
                       breaks=c("2DG", "None"),
                       labels=c("2DG", "Control")) +
  scale_linetype_manual(values=c(1,2))
print(p)
```

## Scree plot and summary statistics small intestine
```{r PCA small.intestine log 96hr}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM.sample.info.small.intestine <- rownames_to_column(tdata.FPKM.sample.info) %>% filter(Tissue=="Small Intestine" & Time=="96 hrs") %>% column_to_rownames('rowname')

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

rows <- rownames(tdata.FPKM.sample.info.small.intestine)

log.tdata.FPKM.small.intestine <- rownames_to_column(log.tdata.FPKM) 

log.tdata.FPKM.small.intestine <- log.tdata.FPKM.small.intestine %>% filter(rowname %in% rows) %>% column_to_rownames('rowname')

pca <- prcomp(log.tdata.FPKM.small.intestine, center = T)

screeplot(pca,type = "lines")

summary(pca)
```

## Treatment small intestine
```{r small.intestine log PCA Treatment 96hr}

Treatment_color <- as.factor(tdata.FPKM.sample.info.small.intestine$Treatment)
Treatment_color <- as.data.frame(Treatment_color)
col_treatment <- colorRampPalette(brewer.pal(n = 12, name = "Paired"))(2)[Treatment_color$Treatment_color]
pca_treatment <- cbind(Treatment_color,pca$x[,1],pca$x[,2])
pca_treatment <- as.data.frame(pca_treatment)

p <- ggplot(pca_treatment,aes(pca$x[,1], pca$x[,2]))
p <- p + geom_point(aes(fill = as.factor(pca_treatment$Treatment_color)), shape=21, size=4) + theme_bw()
p <- p + theme(legend.title = element_text(size=10,face="bold")) + 
  theme(legend.text = element_text(size=10, face="bold"))
p <- p + xlab("PCA 1 (29.82%)") + ylab("PCA 2 (22.72%)") + theme(axis.title = element_text(face="bold"))
p <- p + stat_ellipse(aes(pca$x[,1], pca$x[,2], group = Treatment_color, fill = as.factor(pca_treatment$Treatment_color)), geom="polygon",level=0.95,alpha=0.4) +
  scale_fill_manual(values=c("#A6CEE3", "#B15928"),name="Treatment Type",
                       breaks=c("2DG", "None"),
                       labels=c("2DG", "Control")) +
  scale_linetype_manual(values=c(1,2))
print(p)
```

## Scree plot and summary statistics skeletal muscle
```{r PCA skeletal.muscle log 96hr}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM.sample.info.skeletal.muscle <- rownames_to_column(tdata.FPKM.sample.info) %>% filter(Tissue=="Skeletal Muscle" & Time=="96 hrs") %>% column_to_rownames('rowname')

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

rows <- rownames(tdata.FPKM.sample.info.skeletal.muscle)

log.tdata.FPKM.skeletal.muscle <- rownames_to_column(log.tdata.FPKM) 

log.tdata.FPKM.skeletal.muscle <- log.tdata.FPKM.skeletal.muscle %>% filter(rowname %in% rows) %>% column_to_rownames('rowname')

pca <- prcomp(log.tdata.FPKM.skeletal.muscle, center = T)

screeplot(pca,type = "lines")

summary(pca)
```

## Treatment skeletal muscle
```{r skeletal.muscle log PCA Treatment 96hr}

Treatment_color <- as.factor(tdata.FPKM.sample.info.skeletal.muscle$Treatment)
Treatment_color <- as.data.frame(Treatment_color)
col_treatment <- colorRampPalette(brewer.pal(n = 12, name = "Paired"))(2)[Treatment_color$Treatment_color]
pca_treatment <- cbind(Treatment_color,pca$x[,1],pca$x[,2])
pca_treatment <- as.data.frame(pca_treatment)

p <- ggplot(pca_treatment,aes(pca$x[,1], pca$x[,2]))
p <- p + geom_point(aes(fill = as.factor(pca_treatment$Treatment_color)), shape=21, size=4) + theme_bw()
p <- p + theme(legend.title = element_text(size=10,face="bold")) + 
  theme(legend.text = element_text(size=10, face="bold"))
p <- p + xlab("PCA 1 (61.82%)") + ylab("PCA 2 (10.96%)") + theme(axis.title = element_text(face="bold"))
p <- p + stat_ellipse(aes(pca$x[,1], pca$x[,2], group = Treatment_color, fill = as.factor(pca_treatment$Treatment_color)), geom="polygon",level=0.95,alpha=0.4) +
  scale_fill_manual(values=c("#A6CEE3", "#B15928"),name="Treatment Type",
                       breaks=c("2DG", "None"),
                       labels=c("2DG", "Control")) +
  scale_linetype_manual(values=c(1,2))
print(p)
```

## Scree plot and summary statistics prefrontal cortex
```{r PCA prefrontal.cortex log 96hr}
tdata.FPKM.sample.info <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_phenotypes.RData"))

tdata.FPKM.sample.info.prefrontal.cortex <- rownames_to_column(tdata.FPKM.sample.info) %>% filter(Tissue=="Pre-frontal Cortex" & Time=="96 hrs") %>% column_to_rownames('rowname')

tdata.FPKM <- readRDS(here("Data","20190406_RNAseq_B6_4wk_2DG_counts_numeric.RData"))

log.tdata.FPKM <- log(tdata.FPKM + 1)
log.tdata.FPKM <- as.data.frame(log.tdata.FPKM)

rows <- rownames(tdata.FPKM.sample.info.prefrontal.cortex)

log.tdata.FPKM.prefrontal.cortex <- rownames_to_column(log.tdata.FPKM) 

log.tdata.FPKM.prefrontal.cortex <- log.tdata.FPKM.prefrontal.cortex %>% filter(rowname %in% rows) %>% column_to_rownames('rowname')

pca <- prcomp(log.tdata.FPKM.prefrontal.cortex, center = T)

screeplot(pca,type = "lines")

summary(pca)
```

## Treatment prefrontal cortex
```{r prefrontal.cortex log PCA Treatment 96hr}

Treatment_color <- as.factor(tdata.FPKM.sample.info.prefrontal.cortex$Treatment)
Treatment_color <- as.data.frame(Treatment_color)
col_treatment <- colorRampPalette(brewer.pal(n = 12, name = "Paired"))(2)[Treatment_color$Treatment_color]
pca_treatment <- cbind(Treatment_color,pca$x[,1],pca$x[,2])
pca_treatment <- as.data.frame(pca_treatment)

p <- ggplot(pca_treatment,aes(pca$x[,1], pca$x[,2]))
p <- p + geom_point(aes(fill = as.factor(pca_treatment$Treatment_color)), shape=21, size=4) + theme_bw()
p <- p + theme(legend.title = element_text(size=10,face="bold")) + 
  theme(legend.text = element_text(size=10, face="bold"))
p <- p + xlab("PCA 1 (37.2%)") + ylab("PCA 2 (24.71%)") + theme(axis.title = element_text(face="bold"))
p <- p + stat_ellipse(aes(pca$x[,1], pca$x[,2], group = Treatment_color, fill = as.factor(pca_treatment$Treatment_color)), geom="polygon",level=0.95,alpha=0.4) +
  scale_fill_manual(values=c("#A6CEE3", "#B15928"),name="Treatment Type",
                       breaks=c("2DG", "None"),
                       labels=c("2DG", "Control")) +
  scale_linetype_manual(values=c(1,2))
print(p)
```